\documentclass[sigconf]{acmart}

\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,fit,calc}

\setcopyright{none}
\settopmatter{printacmref=false}
\renewcommand\shortauthors{Skaperdas et al.}

\title{OG-NSD: Neuro-Symbolic Ontology Drafting from Natural-Language Requirements}

\author{Efstratios Skaperdas}
\author{Kristi Cami}
\author{Nick Bassiliades}
\affiliation{%
  \institution{Department of Informatics, Aristotle University of Thessaloniki, Greece}%
  \country{Greece}}

\begin{document}

\begin{abstract}
Natural-language requirements are easy for analysts and domain stakeholders to write, but difficult to validate systematically and to transform into machine-interpretable semantic artifacts. We present \emph{OG-NSD}, a neuro-symbolic pipeline for ontology drafting from natural-language requirements. The pipeline combines LLM-based drafting with ontology-aware prompting, SHACL validation, OWL/DL reasoning, competency-question evaluation, and an iterative repair loop that converts symbolic violations into corrective prompts. We evaluate the approach through a controlled pilot study spanning neural baselines, a validation-oriented baseline, ontology-aware drafting, iterative repair policies, cross-domain transfer, and CQ-oriented iterative analysis. The results show a deliberately mixed but informative picture. Low-temperature drafting provides a strong raw baseline ($F1 = 0.4769$, 11/21 competency questions), ontology-aware prompting improves vocabulary alignment but not necessarily precision, and iterative repair helps only when conservative stopping policies are used. Among the tested repair strategies, the \texttt{max\_only} configuration yields the best balance within the iterative family ($F1 = 0.3427$, 11/21 competency questions), whereas aggressive CQ-driven repair leads to graph explosion and unstable reasoning. These findings support the main claim of the paper: symbolic feedback is most useful when treated as an active control mechanism for ontology drafting rather than as a purely post-hoc diagnostic layer.
\end{abstract}

\keywords{LLMs, ontology engineering, requirements formalization, neuro-symbolic AI, SHACL, OWL}

\maketitle

\input{sections/intro}
\input{sections/related_work}
\input{sections/methodology}
% \input{sections/experimental_setup}
% \input{sections/results}
% \input{sections/discussion}
% \input{sections/threats_to_validity}
% \input{sections/conclusion}

\input{sections/references}

\end{document}

