\section{RESULTS}
\subsection{Ontology Element Extraction}
Table~\ref{tab:table1} reports the precision, recall, and F1--score for ontology element extraction across baselines (exact triple matching). The LLM--only baseline is averaged over two seeds. While the symbolic component achieves the highest recall, the full neuro--symbolic pipeline yields a stronger precision--recall balance than either baseline.

\begin{table}[t]
\centering
\caption{Ontology element extraction quality (exact triple matching).}
\label{tab:table1}
\begin{tabular}{lccc}
\toprule
Method & Precision & Recall & F1 \\
\midrule
LLM-only (avg.\ 2 seeds) & 0.260 & 0.336 & 0.292 \\
Symbolic-only & 0.275 & 0.552 & 0.367 \\
Ours (no repair) & 0.158 & 0.552 & 0.245 \\
Ours (full) & 0.213 & 0.536 & 0.305 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Constraint Compliance and Repair Efficiency}
Table~\ref{tab:table2} summarizes the effect of the repair loop on SHACL compliance and competency question (CQ) satisfaction. For the ATM dataset, both settings already satisfy the SHACL constraints, and the repair loop terminates after two iterations when no hard violations remain. The CQ pass rate remains within the same range (12/21 vs.\ 11/21), indicating that the repair loop in this configuration primarily targets structural validity rather than improving CQ coverage.

\begin{table}[t]
\centering
\caption{Constraint compliance, CQ pass rate, and repair efficiency.}
\label{tab:table2}
\begin{tabular}{lcccccc}
\toprule
Setting & Viol.\ pre & Viol.\ post & CQ passed & CQ pass rate & Iterations & Conforms \\
\midrule
No repair & 0 & 0 & 12/21 & 0.571 & 0 & Yes \\
Full & 0 & 0 & 11/21 & 0.524 & 2 & Yes \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Domain Adaptation}
Table~\ref{tab:table3} reports cross--domain extraction results when switching to the healthcare dataset. Performance degrades substantially compared to ATM, suggesting that domain transfer requires additional adaptation (e.g., richer domain ontologies or more targeted prompting) to maintain extraction quality.

\begin{table}[t]
\centering
\caption{Cross--domain ontology extraction (exact matching).}
\label{tab:table3}
\begin{tabular}{lccc}
\toprule
Domain & Precision & Recall & F1 \\
\midrule
ATM & 0.185 & 0.304 & 0.230 \\
Healthcare & 0.035 & 0.079 & 0.048 \\
\bottomrule
\end{tabular}
\end{table}
