\begin{thebibliography}{12}

\bibitem{gruber1993}
T. R. Gruber.
A translation approach to portable ontology specifications.
\emph{Knowledge Acquisition}, 5(2):199--220, 1993.

\bibitem{uschold1996}
M. Uschold and M. Gr\"{u}ninger.
Ontologies: Principles, methods and applications.
\emph{The Knowledge Engineering Review}, 11(2):93--136, 1996.

\bibitem{gruninger1995}
M. Gr\"{u}ninger and M. S. Fox.
The role of competency questions in enterprise engineering.
In \emph{Benchmarking --- Theory and Practice}, pages 22--31. Springer, 1995.

\bibitem{monfardini2023}
G. K. Q. Monfardini, J. P. A. Almeida, and G. Guizzardi.
Use of competency questions in ontology engineering: A survey.
\emph{Applied Ontology}, 18(1):1--38, 2023.

\bibitem{shacl2017}
H. Knublauch and D. Kontokostas, editors.
\emph{Shapes Constraint Language (SHACL)}.
W3C Recommendation, 2017.

\bibitem{owl2overview2012}
W3C OWL Working Group.
\emph{OWL 2 Web Ontology Language: Document Overview (Second Edition)}.
W3C Recommendation, 2012.

\bibitem{owl2syntax2012}
B. Motik, P. F. Patel-Schneider, and B. Parsia, editors.
\emph{OWL 2 Web Ontology Language: Structural Specification and Functional-Style Syntax (Second Edition)}.
W3C Recommendation, 2012.

\bibitem{garcia2024thesis}
J. Garc\'{i}a Fern\'{a}ndez.
\emph{Ontology Engineering with Large Language Models}.
Master's thesis, Delft University of Technology / TNO, 2024.

\bibitem{saeedizade2024}
M. J. Saeedizade, A. S. Lippolis, M. Poveda-Villal\'{o}n, and O. Corcho.
Navigating ontology development with large language models.
In \emph{Proceedings of ESWC 2024 Workshops}, 2024.

\bibitem{lippolis2024}
A. S. Lippolis, M. J. Saeedizade, M. Poveda-Villal\'{o}n, and O. Corcho.
Ontology generation with metacognitive prompting in large language models.
In \emph{Proceedings of ESWC 2024 Workshops}, 2024.

\bibitem{garijo2025}
D. Garijo, M. Poveda-Villal\'{o}n, E. Amador-Dom\'{i}nguez, Z. Wang, R. Garc\'{i}a-Castro, and O. Corcho.
LLMs for ontology engineering: A landscape of tasks and benchmarking challenges.
In \emph{Proceedings of the 1st International Workshop on LLMs for Ontology Engineering}, 2025.

\bibitem{delong2024}
L. N. DeLong, R. Fern\'{a}ndez Mir, and J. D. Fleuriot.
Neurosymbolic AI for reasoning over knowledge graphs: A survey.
\emph{arXiv preprint arXiv:2302.07200}, 2024.

\end{thebibliography}
